Formalization of Network Flow Algorithms

### 2017-03-02 paper/root.tex
small fix

%change both above and following margins to have consistent indentation
\newenvironment{lstquote}%
  {\list{}{\leftmargin=0.15in\rightmargin=0.15in}\item[]}%
  {\endlist}

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,5,10,25},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $28k$}, 
      yticklabels = {$0.1$, $1$,$5$,$10$,$25$}, 
      smooth,
      cycle list name = black white
	]

>>>>

%%%%%%%%% IMPORTANT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%change both above and following margins to have consistent indentation
\newenvironment{lstquote}%
  {\list{}{\leftmargin=0.15in\rightmargin=0.15in}\item[]}%
  {\endlist}

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,5,10,20},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $28k$}, 
      yticklabels = {$0.1$, $1$,$5$,$10$,$20$}, 
      smooth,
      cycle list name = black white
	]
